Using Monte Carlo Algorithms to Achieve Resiliency \& Performance at Scale for Linear and Nonlinear Solver Applications

### 2016-01-26 doc/ecp/pres.tex
Added scaling plots.

>>>>

\begin{frame}{Scaling - DD}

  \begin{figure}
    \centering
    \begin{tabular}{cc}
      \subfigure[Strong time]{\includegraphics[width=1.8in]{strong_dd_time}} &
      \subfigure[Strong efficiency]{\includegraphics[width=1.8in]{strong_dd_eff}} \\
      %%
      \subfigure[Weak time]{\includegraphics[width=1.8in]{weak_dd_time}} &
      \subfigure[Weak efficiency]{\includegraphics[width=1.8in]{weak_dd_eff}} \\
    \end{tabular}
  \end{figure}
\end{frame}

\begin{frame}{Scaling - Replication}

  \begin{figure}
    \centering
    \begin{tabular}{cc}
      \subfigure[Strong time]{\includegraphics[width=2in]{strong_rep_time}} &
      \subfigure[Strong efficiency]{\includegraphics[width=2in]{strong_rep_eff}} \\
      %%
    \end{tabular}
  \end{figure}
